Propositions as Sessions, Mechanically

### 2015-04-11 paper/formalisation.tex
Added figure to discussion on type kind representation.

On a more technical note, all types are amalgamated into one inductive
definition and provide a predicate for restricting typing rules to consider
only valid session types. \citeauthor{Wadler:2014} defines GV types as a set
of mutually recursive definitions; session types are types which may contain
types as subcomponents (arguments to send, for example). Unfortunately,
handling mutually inductive definitions in Coq can be quite involved,
requiring one to either rely on the Coq system to provide a stronger mutual
induction principle or defining one manually. Such a definition is possible,
but it complicates applications of the induction principle.

Another issue related to types is how to represent type kinds, linear and
unlimited kind. Initially the type definition was indexed by the kind and
while this definition has the advantage of preventing certain ill-formed
types, such as a non-linear session type, it complicated later definitions and
proofs. For instance, the decidability of equality on types now relied on an
axiom permitting heterogeneous equality~\cite{McBride:1999}. Generally, it is
better to avoid unnecessary postulates if possible. Further, when formulating
the typing rules, the kind must be given to each type hypothesised and most
rules (e.g. \coqe!wt_tm_labs!) are polymorphic in the kind, requring an
awkward kind inspection function to be applied to each type within a
binding. The alternative approach taken was to define a well-formed type
relation and remove the kind index from the type definition. These issues
highlighted that one should be careful and considerate regarding when to use
dependent types. These issues highlighted that one should take care over the
representation and its effect on later expressiveness.

>>>>

All types are amalgamated into one inductive definition and provide a
predicate for restricting typing rules to consider only valid session
types. As shown in \S~\ref{sec:...}, \citeauthor{Wadler:2014} defines GV types
as a set of mutually recursive definitions. Unfortunately, handling mutually
inductive definitions in Coq can be quite involved, requiring one to either
rely on the Coq system to provide a stronger mutual induction principle or
define one manually. Such a definition is possible, but it complicates
applications of the induction principle.

\input{wft}

Another issue related to types is how to represent type kinds, linear and
unlimited kind. Initially the type definition was indexed by the kind and
while this definition has the advantage of preventing certain ill-formed
types, such as a non-linear session type, it complicated later definitions and
proofs. For instance, the decidability of equality on types now relied on an
axiom permitting heterogeneous equality~\cite{McBride:1999}. Generally, it is
better to avoid unnecessary postulates if possible. Further, when formulating
the typing rules, the kind must be given to each type hypothesised and most
rules are polymorphic in the kind, requring an awkward kind inspection
function to be applied to each type within a binding. The alternative approach
taken was to define a well-formed type relation and remove the kind index from
the type definition. Figure~\ref{fig:wft} shows the well-formedness for the
linear function type. Notice, that even though the conclusion must have linear
kind, as in rule \coqe!wt_tm_labs!, the argument and result types can have any
kind, highlighting the aforementioned kind polymorphism. These issues
highlighted that one should be careful and considerate regarding when to use
dependent types. These issues highlighted that one should take care over the
representation and its effect on later expressiveness.
